---
title: "R Markdown Presentation & Plotly Assignment (Week 3)"
author: "Faylene Gilles"
date: '27th March 2019'
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Course Work

The task is to create a web page presentation using R Markdown that features a plot created with Plotly. This presentation is hosted on GitHub Pages.

On the following plot we can explore relationship between mammals sleep cycle (hours) and their brain weight (kg). Respective mammals names are presented hovering the plot.  

## Mammals Sleep Cycle and Brain Weight

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(plotly)
sleep_data <- as.data.frame(msleep)
p <- plot_ly(sleep_data, x = ~sleep_cycle, y = ~brainwt, type = 'scatter', text = ~name,
             marker = list(size = 10, color = "darkgreen")) %>%
        layout(title = 'Mammals Sleep Cycle and Brain Weight',
               xaxis = list(title = 'Sleep Cycle (hours)'),
               yaxis = list(title = 'Brain Weight (kg)'))
p
```

